---
title: "Lab 3"
author: "Jing Zhao, Gulzina Kuttubekova, Agadilov Gani, Joshua Budi"
date: "3/13/2019"
output: rmarkdown::github_document
always_allow_html: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, messsage = FALSE, warning = FALSE)
```

The package stat585lab3package was created for lab3 in STAT 585. This package contains four functions (team_1,team_10,team_11,?) which can convert sf shape files to data frames. These functions are based on lab 2 activity in the stat585. 

Here is a link to our GitHub \
[Link](https://github.com/kgulzina/stat585lab3package) to the github repo where all code of the package is deposited.


First, load the package.
```{r}
library(stat585lab3package)
```


# Functions
## team_1
The team_1 was written by Gani Agadilov. This is the function created by team 1 in lab2 activity.\
``input``\
file: file path is a file path to a shape file\
tolerance: value used for thinning the polygon
```{r}
# Aus_t1 <- team_1("./data/gadm36_AUS_shp/gadm36_AUS_1.shp", 0.1)
# head(Aus_t1)
```

## team_10
The team_10 function was written by Gulzina Kuttubekova. This is the function created by team 10 in lab2 activity.\
``input``\
file: file path to a shapefile\
tolerance: tolerance
`Value`
geo_info: dataframe containing geographic and additional information on polygons.
```{r}
Aus_t10 <- team_10("./data/gadm36_AUS_shp/gadm36_AUS_1.shp",0.1)
head(Aus_t10)
```

## team_11

The team_11 function was written by Jing Zhao. This is the function created by team 11 in lab2 activity.\

``input``\
 file : input shape file datsest (.shp)\
 tolerance:  the value for thining the shape file. The tolerance is a single numeric value (e.g., 0.1)

```{r}
# Use the team_11 function to convert the shape file to a dataframe using example data
Aus_t11 <- team_11("./data/gadm36_AUS_shp/gadm36_AUS_1.shp",0.1)
# pring the head of the dataframe
head(Aus_t11)
```


We also creat an example data within the package called (Aus) using the following code.
```{r message = FALSE}
#convert shape file to sf file
library(tidyverse)
library(sf)
# Read in the shape file
ozbig <- read_sf("./data/gadm36_AUS_shp/gadm36_AUS_1.shp")
# Thin the file
oz_st <- maptools::thinnedSpatialPoly(as(ozbig, "Spatial"), 
                                      tolerance = 0.1, 
                                      minarea = 0.001, 
                                      topologyPreserve = TRUE)
# Convert it to a sf file
Aus <- st_as_sf(oz_st)
```
The same result yielded using this function.
```{r}
Aus_t11_2 <- team_11(Aus, 0.1)
head(Aus_t11_2)
```





