---
title: "Lab 3"
author: "Jing Zhao, Gulzina Kuttubekova, Agadilov Gani, Joshua Budi"
date: "3/13/2019"
output: rmarkdown::github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, messsage = FALSE, warning = FALSE)
```

The package stat585lab3package was created for lab3 in STAT 585. This package contains four functions (team_1,team_10,team_11,?) which can convert sf shape files to data frames. These functions are based on lab 2 activity in the stat585. 

Here is a link to our GitHub 
[Link](https://github.com/kgulzina/stat585lab3package) to the github repo where all code of the package is deposited.

Load the package.
```{r}
library(stat585lab3package)
```

# Functions
## team_1
The team_1 was written by Gani Agadilov. This is the function created by team 1 in lab2 activity.
`input`
file: file path is a file path to a shape file
tolerance: value used for thinning the polygon

## team_10
The team_10 function was written by Gulzina Kuttubekova. This is the function created by team 10 in lab2 activity.
`input`
file:file path to a shapefile
tolerance: tolerance
`Value`
geo_info: dataframe containing geographic and additional information on polygons.

## team_11

The team_11 function was written by Jing Zhao. This is the function created by team 11 in lab2 activity.

`input`
 file : input shape file datsest (.shp)
 tolerance:  the value for thining the shape file. The tolerance is a single numeric value (e.g., 0.1)

# Use the team_11 function to convert the shape file to a dataframe using example data
# pring the head of the dataframe
```{r}
Aus_datfra <- team_11(Aus, 0.1)
head(Aus_datfra)
```





